---
title: "Overlaps organoids and fetal single cell clusters"

author:
- name: Author Nicolò Caporale (nicolo.caporale@ieo.it)
- name: Note the multintersect function was written by Pierre-Luc Germain (pierre-luc.germain@ieo.it)

date: 'Date: `r format(Sys.Date(), "%B %d, %Y")`'
output:
    html_document:
        toc: true
        toc_float: true
        theme: 'simplex'
        highlight: 'espresso'
        #code_folding: hide
---



## Data loading

For details on data preparation look [here](./DataPreparation/Internal/DataPreparation.html) for Internal Organoids clusters

***
[here](./DataPreparation/Nowakowski_et_al/DataPreparation.html) for Nowakowski_et_al clusters

***
and [here](./DataPreparation/Nowakowski_et_al/DataPreparation.html) for Amiri_et_al clusters

```{r, warning=FALSE, message=FALSE}
source("Functions/PaperCHIRfunctions.R")
load("Data/Nowakowski_et_al.RData")
load("Data/Amiri_et_al.RData")
load("Data/Internal.RData")
load("Data/universe.RData")
```


## Overlaps internal (clusters) vs Nowakowski_et_al (selected meaningful clusters)
```{r,warning=FALSE,message=FALSE,fig.height=7,fig.width=8}
multintersect(ClusterInternal, ClusterNowakowskiSelected,universe = universe)
```


## Overlaps internal (cell populations) vs Amiri_et_al (selected meaningful clusters)
```{r, warning=FALSE,message=FALSE, fig.height=7,fig.width=8}
multintersect( ClusterInternalArea, ClusterAmiriSelected,universe = universe)
```


