---
date: 'Date: `r format(Sys.Date(), "%B %d, %Y")`'
output:
    html_document:
        toc: true
        toc_float: true
        theme: 'simplex'
        highlight: 'espresso'
        #code_folding: hide
---



To go back to the main page go [here](../../Overlap.html)


## Data preparation
From the differential expression analysis of single nuclei clusters (Table S6 of the paper by Amiri et al, DOI: 10.1126/science.aat6720), I create a list with the significant upregulated genes for each cluster

```{r, warning=FALSE, message=FALSE}
library(readxl)
Genes<- list()
a<- read_excel("aat6720_Table_S6.xlsx",sheet= "Cell Type Markers (c)")
b<- read_excel("aat6720_Table_S6.xlsx",sheet= "Cluster Cell Frequency (b)")
colnames(b) <- b[1,]
b <- b[-1,]

Cluster0 <- as.character(a$gene[which(a$cluster == 0 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster1 <- as.character(a$gene[which(a$cluster == 1 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster2 <- as.character(a$gene[which(a$cluster == 2 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster3 <- as.character(a$gene[which(a$cluster == 3 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster4 <- as.character(a$gene[which(a$cluster == 4 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster5 <- as.character(a$gene[which(a$cluster == 5 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster6 <- as.character(a$gene[which(a$cluster == 6 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster7 <- as.character(a$gene[which(a$cluster == 7 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster8 <- as.character(a$gene[which(a$cluster == 8 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster9 <- as.character(a$gene[which(a$cluster == 9 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster10 <- as.character(a$gene[which(a$cluster == 10 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster11 <- as.character(a$gene[which(a$cluster == 11 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster12 <- as.character(a$gene[which(a$cluster == 12 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster13 <- as.character(a$gene[which(a$cluster == 13 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])
Cluster14 <- as.character(a$gene[which(a$cluster == 14 & a$p_val_adj<0.05 & a$avg_logFC>log2(1))])

ClusterAmiriAll <- list(Cluster0=Cluster0,Cluster1=Cluster1,Cluster2=Cluster2,Cluster3=Cluster3,Cluster4=Cluster4,Cluster5=Cluster5,Cluster6=Cluster6,Cluster7=Cluster7,Cluster8=Cluster8,Cluster9=Cluster9,Cluster10=Cluster10,Cluster11=Cluster11,Cluster12=Cluster12,Cluster13=Cluster13,Cluster14=Cluster14)
names(ClusterAmiriAll) <- b$`Proposed Name`[1:15]
```

## Cluster selection
Here I only select the clusters that are more relevant for our cortical brain organoids
```{r}
ClusterAmiriSelected <- ClusterAmiriAll
ClusterAmiriSelected$`Unknown 1 (U1)`<-NULL
ClusterAmiriSelected$`Unknown 4 (U4)`<-NULL
ClusterAmiriSelected$`Unknown 3(U3)/Glyc`<-NULL
ClusterAmiriSelected$`Inhibitory/excitatory neurons (IN/EN)`<-NULL
ClusterAmiriSelected$`Oligodendrocyte progenitors (OPC)`<-NULL
ClusterAmiriSelected$`ventRG/outerRG/Astrocytes`<-NULL

save(ClusterAmiriAll, ClusterAmiriSelected, file = "../../Data/Amiri_et_al.RData")
```



